Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-01 AAMAS2021/minimax.tex
anonymous
chair
Merged prop abstract

\documentclass[sigconf]{aamas} 
%\documentclass[sigconf,anonymous]{aamas}

@@

\begin{abstract}
Social choice deals with the problem of determining a consensus choice from the preferences of different agents (voters).
In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided. However, requiring the agents to express full preference orderings can be costly, and formalizing a voting rule it is not an easy task. Methods for eliciting the voting rule when the preferences of the agents are completely known have been proposed, as well as techniques that consider the opposite scenario.
However, both of them may be unknown.
This paper addresses this case, and proposes a method which permits to obtain recommendations without requiring full knowledge of either.
Focusing on positional scoring rules, we assume that the chair, while  not able to give a precise definition of the rule, is capable of answering simple questions  requiring to pick a winner from a specific  example profile. Moreover, the preferences of the agents are incrementally acquired by asking comparison queries.
In this setting, we propose a method  for robust approximate winner determination with minimax regret. We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that interleave questions to the chair and questions to the agents in order to attempt to acquire the most relevant information in order to quickly converge to optimal or a near-optimal alternative. 
\end{abstract}

@@

The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents are expressed beforehand. These represent two strong hypothesis.
Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agent preferences. \\ Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method. Thus, the first hypothesis should also be relaxed. 
%Also the first hypothesis should be relaxed considering that, in several situations, it may not be easy to precisely define the voting rule.Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.

@@

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
			\midrule
			0 & 5.02 & 0.82 & 3.21 & 1.6 \\
			25 & 5.83 & 1.25 & 6.79 & 1.2 \\
			50 & 6.47 & 1.14 & 5.2 & 1.58 \\
			100 & 9.4 & 1.58 & 8.66 & 0.51 \\
			150 & 11.89 & 1.1 & 12.31 & 0.96 \\
			200 & 15.64  & 0.52 & 16.12 & 1.06 \\
			250 & 20.0 & 0.0 & 20.0 & 0.0 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average regret in problems of size $(10, 20)$ after $250$ questions over $5$ runs. Where $p$ represents the number of questions asked to the committee.}
	\label{fig:p}
\end{table}

>>>>

%\documentclass[sigconf]{aamas} 
\documentclass[sigconf, anonymous]{aamas}

@@

\begin{abstract}
Social choice deals with the problem of determining a consensus choice from the preferences of different agents.
In the classical setting, the voting rule is fixed beforehand and full information concerning the preferences of the agents is provided.
This assumption of full preference information has recently been questioned by a number of researchers.
Methods for eliciting the voting rule when the preferences of the agents are completely known have been proposed, as well as techniques that consider the opposite scenario. %, viewing the voting rule as representing the preference of the chair. 
This article goes one step further by tackling one important new case, namely, when both the voting rule and the agents preferences are partially known. It also permits to obtain a progressively refined recommendation without requiring to achieve full knowledge of either sort of information.
%However, there may be cases where both of them are only partially known.
%This paper considers both sources of uncertainty at the same time, and proposes a method able to recommend a consensus choice without requiring full knowledge of either.
This is useful because providing such information is often costly: the chair may find it hard to specify a rule completely; voters may need time to form reflective preferences.
Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile. In addition, the preferences of the agents are incrementally acquired by asking comparison queries. 
In this setting, we propose a method for robust approximate winner determination with minimax regret. We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative.
\end{abstract}

@@

The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (voters) are expressed beforehand. These represent two strong hypothesis.
Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agent preferences. \\ Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method. Thus, the first hypothesis should also be relaxed. 
%Also the first hypothesis should be relaxed considering that, in several situations, it may not be easy to precisely define the voting rule.Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.

@@

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
			\midrule
			0 & 5.02 & 0.82 & 3.21 & 1.6 \\
			25 & 5.83 & 1.25 & 6.79 & 1.2 \\
			50 & 6.47 & 1.14 & 5.2 & 1.58 \\
			100 & 9.4 & 1.58 & 8.66 & 0.51 \\
			150 & 11.89 & 1.1 & 12.31 & 0.96 \\
			200 & 15.64  & 0.52 & 16.12 & 1.06 \\
			250 & 20.0 & 0.0 & 20.0 & 0.0 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average regret in problems of size $(10, 20)$ after $250$ questions over $5$ runs. Where $p$ represents the number of questions asked to the chair.}
	\label{fig:p}
\end{table}
